\documentclass[margin,line]{resume}

\usepackage{hyperref}

\usepackage[usenames,dvipsnames]{xcolor}

%\hypersetup{colorlinks=false}

 

\hypersetup{

bookmarks=true, % show bookmarks bar?

unicode=false, % non-Latin characters in Acrobat’s bookmarks

pdftoolbar=true, % show Acrobat’s toolbar?

pdfmenubar=true, % show Acrobat’s menu?

pdffitwindow=false, % window fit to page when opened

pdfstartview={FitH}, % fits the width of the page to the window

pdftitle={My title}, % title

pdfauthor={Author}, % author

pdfsubject={Subject}, % subject of the document

pdfcreator={Creator}, % creator of the document

pdfproducer={Producer}, % producer of the document

pdfkeywords={keyword1} {key2} {key3}, % list of keywords

pdfnewwindow=true, % links in new window

colorlinks=true, % false: boxed links; true: colored links

linkcolor=red, % color of internal links

citecolor=green, % color of links to bibliography

filecolor=magenta, % color of file links

urlcolor=NavyBlue % color of external links

}

 

%______________________________________________________________________________________________________________________

\begin{document}

\name{\Large \hspace{26.0mm} John Doe} %\small \texttt{junk@mail.com}

\begin{resume}

\vspace{-3mm}

\texttt{\href{mailto:email_address}{mail@gmail.com}}

%__________________________________________________________________________________________________________________

% Contact Information

%\section{\mysidestyle Contact\\Information}

 

%__________________________________________________________________________________________________________________

% Education

\section{\mysidestyle Education}

\textbf{University of School}, City, State \vspace{0mm}\\\vspace{1mm}%

\textsl{Major of Basketweaving} \hfill

\textbf{Expected Graduation Date:} \vspace{-3mm}\\\vspace{-1mm}%

\begin{list2}

\item Cumulative GPA: \textbf{3.813} \hfill \textbf{Spring 2014 \hspace{3mm} }

\item Technical GPA: \textbf{3.769}

% \item Expected graduation date: Spring 2014


\end{list2}\vspace{-1.5mm}

%__________________________________________________________________________________________________________________

% Courses

\section{\mysidestyle Technical Courses}

% note to reddit: classes go here

\begin{tabular}{ l l }

\textbf{Electrical Engineering} & \textbf{Other Technical Classes} \\

XXXX: Name of class& Name of class \\

XXXX: Name of class& Name of class \\

XXXX: Name of class& Name of class \\

XXXX: Name of class& Name of class \\

XXXX: Name of class& Name of class

\end{tabular}

%__________________________________________________________________________________________________________________

% Computer Skills

\section{\mysidestyle Programming}

C/C++, Objective-C, Python, MATLAB, Mathematica, Scheme, Unix shell scripting

%__________________________________________________________________________________________________________________

% Research Experience

\section{\mysidestyle Research\\Experience}

\textbf{Research Expirence} \vspace{0mm}\\\vspace{1mm}%

\textsl{Mentor: Susan Lee} \hfill \textbf{Spring 2012}\\ An The joint RD agreement may be subject to the competition rules. The European Commission and other EU/EEA institutions are encouraging RD by making exceptions to the strict competition rules in a Regulation on a block


\textbf{Research Expirence Name} \vspace{0mm}\\\vspace{1mm}%

\textsl{Mentor: Getoff Droff} \hfill \textbf{Fall 2011}\\ The joint RD agreement may be subject to the competition rules. The European Commission and other EU/EEA institutions are encouraging RD by making exceptions to

\textbf{Yet Anthoer Name}

\vspace{0mm}\\\vspace{1mm}% \textsl{Research Assistant} \hfill

\textbf{Summer 2011}\\

The joint RD agreement may be subject to the competition rules. The European Commission and other EU/EEA institutions are encouraging D by making exceptions to the strict competition rules in a Regulation on a block exemption. The Regulation contains the information what should be avoided and provides a blacklist of provisions. The Regulation may not necessarily cover the entire agreement (e.g. price fixing, market sharing and limitation of production and others), due to the some restrictions on competition.


\textbf{Birthday Lane, Happy Dance} \vspace{0mm}\\\vspace{1mm}%

\textsl{Mentor: Notice that trick up there?} \hfill \textbf{Spring 2011}\\

The joint RD agreement may be subject to the competition rules. The European Commission and other EU/EEA institutions are encouraging RD by


%__________________________________________________________________________________________________________________

% Leadership/Student Groups

\section{\mysidestyle Student Groups}

 
\textbf{The Happy Skipper Dance} \vspace{0mm}\\\vspace{0mm}%

\textsl{King of Dancing } \hspace{10mm} \textbf{Fall 2010 -- current}%\\

 
\textbf{Penguins} \vspace{0mm}\\\vspace{0mm}%

\textsl{Ice Queen} \hspace{10mm} \textbf{Fall 2011 -- current}\\

% this vspace{} made the page break bad.

%\vspace{-6mm}

%__________________________________________________________________________________________________________________

% Honours and Awards

\section{\mysidestyle Honors and\\Awards}

Scholarship 1 \vspace{1mm}\\

Scholarship 2: yesterday -- current \vspace{1mm}\\

%______________________________________________________________________________________________________________________

\end{resume}

\end{document}
